Environmental Parameters

### 2023-04-29 code/analysis_code/analysis_README.Rmd
Edits for Manuscript Review
made edsits to analaysis readme

This folder contains code for analyzing cleaned data sets and aids in visualization of parameters of interest.\
(1) The dust subfolder contains `daily_dust.qmd`, which looks at dust concentration over the daily time series. It also contains `dust_and_copies.qmd` which combine Vibrio enumeration with dust data.\
(2) The env sub-folder contains `env_par.qmd` that examines temperature and salinity over the time series.\
(3) The qPCR sub-folder contains `daily_qmd` that has data on Vibrio enumeration. This is also seen in the `dust_and_copies.qmd` in the dust subfolder \
(4) The stats folder contains:
- `distributiom.qmd`: Checks distribution of variables of interest
- `multi_variate.qmd`: runs multivariate models on variable of interest (copies_mL)
- `uni_variate.qmd` : runs univariate models on variable and predictors of interest.

>>>>

---
editor_options: 
  markdown: 
    wrap: 72
---

This folder contains code for analyzing cleaned data sets and aids in
visualization of parameters of interest.\
(1) `dust` folder

-    `daily_dust.qmd`: looks at dust concentration over the daily time
    series. It also contains

-   `dust_and_copies.qmd:` combines Vibrio enumeration with dust data.

\
(2) The `environment` folder

-    `env_par.qmd`: examines environmental parameters of interest.

\
(3) The `qPCR` folder

-    `daily_qmd`: has data on Vibrio enumeration. This is also seen in
    the `dust_and_copies.qmd` in the dust subfolder

\
(4) The `stats` folder:

-    `1_distributiom.qmd`: Checks distribution of variables of interest

-   `2_cca.qmd`: Performs cross-correlation analysis to test for lags in
    time series (between dust input and Vibrio growth)

-    `3_correlation.qmd`: Runs Correlation matrices on all variables

-    `4_uni_variate.qmd` : runs univariate models on variable and
    predictors of interest.

-    `5_multi_variate_models folder`: Contains scripts that runs
    multivariate models on variable of interest (copies_mL) and random
    forest models.
